Nic Steyn

### 2025-09-26 site/index.qmd
updated publications

My thesis focuses on robust statistical methods for analysing infectious disease dynamics with an emphasis on flexible methodology and [valid uncertainty quantification](https://github.com/nicsteyn2/RobustRtEstimators). My research combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/), and epidemiological modelling, with applications to standard epidemiological data, as well as survey data and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).

>>>>

My thesis focuses on robust statistical methods for analysing infectious disease dynamics with an emphasis on **uncertainty quantification**. Recent work has included developing a theoretical/philosophical decision-theoretic framework targeted for the practicalities of epidemiology ([see our preprint here](https://doi.org/10.48550/arXiv.2509.20013)), and extending existing popular methods in the field to improve the robustness of their UQ ([see our published paper here](https://doi.org/10.1093/aje/kwaf165)).

Further research from my thesis combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/) ([see also](https://doi.org/10.1002/sim.70204)), and epidemiological modelling, with applications to standard epidemiological data, as well as [survey data](https://doi.org/10.1101/2025.04.16.25325936) ([see also]((https://doi.org/10.1101/2025.03.03.25323250))) and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).

### 2025-09-26 site/papers.qmd
updated publications

@@

**Steyn, N.**,  Parag, K. V., Thompson, R. N., & Donnelly, C. A. (2025). A primer on inference and prediction with epidemic renewal models using sequential Monte Carlo methods. *Accepted at Statistics in Medicine*. Preprint accessible here: [https://doi.org/10.48550/arXiv.2503.18875](https://doi.org/10.48550/arXiv.2503.18875)

**Steyn, N.**, Chadeau-Hyam, M., Elliott, P., & Donnelly, C. A. (2025). Bayesian modelling of repeated cross-sectional epidemic prevalence survey data. *medRxiv preprint*. [https://doi.org/10.1101/2025.04.16.25325936](https://doi.org/10.1101/2025.04.16.25325936)

**Steyn, N.**, Unwin, H. J. T., Ponmattam, J., et al. (2025). Regional and national estimates of children affected by all-cause and COVID-19-associated orphanhood and caregiver death in Brazil, by age and family circumstance. *medRxiv preprint*. [https://doi.org/10.1101/2025.01.31.25321479](https://doi.org/10.1101/2025.01.31.25321479)

>>>>

**Steyn, N.**,  Parag, K. V., Thompson, R. N., & Donnelly, C. A. (2025). A primer on inference and prediction with epidemic renewal models and sequential Monte Carlo. *Statistics in Medicine*. [https://doi.org/10.1002/sim.70204](https://doi.org/10.1002/sim.70204)

**Steyn, N.**, Chadeau-Hyam, M., Elliott, P., & Donnelly, C. A. (2025). Bayesian modelling of repeated cross-sectional epidemic prevalence survey data. *Accepted in PLOS Computational Biology*. Preprint available here: [https://doi.org/10.1101/2025.04.16.25325936](https://doi.org/10.1101/2025.04.16.25325936)

**Steyn, N.**, Unwin, H. J. T., Ponmattam, J., et al. (2025). Regional and national estimates of children affected by all-cause and COVID-19-associated orphanhood and caregiver death in Brazil, by age and family circumstance. *Accepted in The Lancet Regional Health Americas*. Preprint available here: [https://doi.org/10.1101/2025.01.31.25321479](https://doi.org/10.1101/2025.01.31.25321479)

@@

**Steyn, N.**, Bickford Smith, F., Mills, C., et al. (2025). A decision-theoretic framework for uncertainty quantification in epidemiological modelling. *arXiv preprint*. [https://doi.org/10.48550/arXiv.2509.20013](https://doi.org/10.48550/arXiv.2509.20013)
